Boosted

### 2015-10-26 boost_tree.rmd
moving on from boosted

>>>>

#compact JD.Second into less categories

all9a$Business<- as.character(all9a$Business)
all9a$Business <- ifelse(grepl("lawyer|body", all9a$Business), 
                     "lawyer_bodyC", all9a$Business)
all9a$Business <- ifelse(grepl("univ|school", all9a$Business), 
                     "uni_school", all9a$Business)
all9a$Business <- ifelse(grepl("sign|manuf", all9a$Business), 
                     "sign_manufac", all9a$Business)
all9a$Business <- ifelse(grepl("environ|water", all9a$Business), 
                     "enviro_water", all9a$Business)
all9a$Business <- ifelse(grepl("road|gov|util", all9a$Business), 
                     "road_rail_gov_util", all9a$Business)
all9a$Business <- ifelse(grepl("artist|landscape", all9a$Business), 
                     "artist_landarch", all9a$Business)
all9a$Business <- ifelse(grepl("hospit|institut|health", all9a$Business), 
                     "hosp_institut_health", all9a$Business)
all9a$Business <- ifelse(grepl("business|building|internal", all9a$Business), 
                     "biz_bldgserv_internal", all9a$Business)

all9a$Business<- as.factor(all9a$Business)

write.csv(all9a, 'C:/Users/n9232371/Documents/Consultbusiness/data/all9c.csv') # c for compacted variables
all9c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9c.csv')[,-1]

var.seq<-c("no.users + Business", 
           "no.users")

#make fresh random sample of data
set.seed(200)
sample<- sample(1:nrow(all9c), 2/3*nrow(all9c), replace=F)
train<- all9c[sample,]
test<- all9c[-sample,]

for(i in 1:1){

        fit<-gbm(as.formula(formula), 
                 data=train, distribution="bernoulli", n.trees= 10000,
                 shrinkage=0.001,interaction.depth=4,
                 n.minobsinnode = 20)
        pred<- predict(fit, test, n.tree=10000, type="response")

# Business helps!!!!!!!!

Tune again with caret package, INCLUDING Business category.

#create test train
sample<- sample(1:nrow(all9c), 2/3*nrow(all9c), replace=F)
train<- all9c[sample,]
test<- all9c[-sample,]

formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + inv.mlsto.log +
client.totinv.log + pc.majpos.log + Billing.Type + majority.pos + Business"

cv.Control <- trainControl(method = "cv",
                           number = 5,
                           seeds= seeds
                           , summaryFunction=twoClassSummary,
                           classProbs=TRUE
                           )
gbmGrid <- expand.grid(shrinkage = c(0.001),
                       n.trees = c(10000), interaction.depth = c(1,2,3,4,5),
                       n.minobsinnode = c(10,20,30,40))
set.seed(2)
gbmFit <- train(as.formula(formula), data= train2,
                 method = "gbm", trControl = cv.Control, verbose = FALSE,
                 bag.fraction = 0.5, tuneGrid = gbmGrid,
                metric = 'ROC',
                na.action = na.pass)

# therefore:
# shrinkage = 0.001
# no trees = 10000
# min terminal node size = 20
# max tree depth = 4

# AUC approx 0.770 in 5 fold CV

Does the boosted tree perform better with a subset of the data based on later years?

formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + inv.mlsto.log +
client.totinv.log + pc.majpos.log + majority.pos + Business"

Year.lim <- c(2000, 2004, 2006, 2008, 2009, 2010)
conf.matrix<- list('1' = data.frame(c(0,0), c(0,0)), '2' = data.frame(c(0,0), c(0,0)),
                   '3' = data.frame(c(0,0), c(0,0)), '4' = data.frame(c(0,0), c(0,0)),
                   '5' = data.frame(c(0,0), c(0,0)), '6' = data.frame(c(0,0), c(0,0)))
auc<- rep(list(rep(0,8)),6)
colours <- c("red", "yellow", "green", "blue", "purple", "pink")

        #set up train and test
        set.seed = 100
        subset = all9c %>% filter(Year> Year.lim[i])
        sample<- sample(1:nrow(subset), .75*nrow(subset), replace=F)
        train<- all9c[sample,]
        test<- all9c[-sample,]
        #set up 10 fold cv using caret function
        folds <- createFolds(train$b.rpdol, k=8, list=T, returnTrain=F)
        #now have folds[[1]] through folds[[5]] list of rows to exclude

        for (j in 1:8){
                #make boosted tree
                fit<-gbm(as.formula(formula), 
                         data=train[-folds[[j]],], distribution="bernoulli", n.trees= 10000,
                         shrinkage=0.001,interaction.depth=4,
                         n.minobsinnode = 20)

conf.matrix
auc
saveRDS(auc, 'C:/Users/n9232371/Documents/github/consult/finalwriteup/images/boosted tree/Year_vary_cv.rds')

a<- ggplot(melt(auc), aes(x= factor(L1), y= value)) + geom_boxplot()

# All years are required! Gives the best result
```
